The K2 Bright Star Survey

### 2019-05-16 paper/ms.tex
jie is coauthor

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).

>>>>

\author[0000-0002-0007-6211]{Jie Yu}
\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}

@@

% do hot star asteroseismology and red giants as benchmarks, interferometry
Some of the objects presented here are the subject of more detailed work in preparation, namely Spica (Buzasi et al., in prep.), interferometry of the Hyades giants (White et al., in prep.), and main-sequence stars (Greklek-McKeon et al., in prep.).
